Amicus Word Count

### 2022-01-11 data-cleaning/01-shorten-amicus-text.Rmd
notes

```{r}
alternate_rmv %>% select(id,alternative)
```
Shorten

@@

# Check isntances of "Appendix" or "Footnotes"

@@

@@

Process:

0. Check if "footnotes" is within three words of "omitted" -> in this case, do not remove any text.
1. Ignore instances of "footnotes" in our exceptions:
    * 861810659757"
    * 861821999947 (ignore first instance, second instance is footnotes)
    * 861823138310
    * 861811382099
    * 861820447683
2. If "footnotes" is referenced one time, remove all text after this reference
3. If "footnotes" is mentioned more than once, remove text after the first reference

@@

```{r}
box_write(amicus,
          file_name = "shortened-amicus-brief-text.csv",
          dir_id = 145990409196)
```

>>>>

```{r}
alternate_rmv %>% select(id,alternative)
```

Remove text before summary of argument (already done)

@@

# Check instances of "Appendix" or "Footnotes"

@@

# Remove appendices instances

From undergrad assistant: "I have found that often, the appendix will start with an asterisk (usually *1A Appendix). The Appendix also almost always immediately precedes the footnotes."

We need to:

1. find instances of "*1A Appendix" in the text 
2. Check that this only occurs 1x in a doc. 
3a. If 2) is true, then remove text after these instances.
3b. If 3) is false, further inspect the text (may require manual removal)
4. If it does not occur at all, check for the marker for footnotes (see next section). 
5a. If footnote marker exists, remove all text after
5b. If footnote marker does not exist, then manually inspect text. If there are footnotes/appendix, insert flag into text: "MNOPQRST" (w/o quotes) and remove all text after that flag.

```{r}
brief_names <- amicus %>% 
  arrange(case,brief) %>% 
  mutate(docname = paste0("text", 1:n())) %>%
  select(brief, id, docname)

# get context around "footnotes"
appendix_context <- get_context(x = amicus$txt_short, target = "appendix", 
                                 window = 5, valuetype = "fixed",
                                 case_insensitive = T, hard_cut = F, verbose = F)

appendix_context <- brief_names %>%
  left_join(., appendix_context, by = "docname")
```

Look for *1a

```{r}
appendix_context %>% filter(grepl("* 1a", context))
```

```{r}
amicus %>% filter(grepl("\\* 1a appendix|*", txt_short)) #%>% select(brief)
```

@@

@@

```{r}
#box_write(amicus,
#          file_name = "shortened-amicus-brief-text.csv",
#          dir_id = 145990409196)
```
